\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-05-05 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates
Updates: Removing errors with figures and citations. Still missing figures references

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_fixed_100.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_adapt_start.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
}
}     
\caption{Comparing test-cases of fixed and adaptive mesh while we have a dual inlet, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps}
\label{fig:3testcase_a}
\end{figure}

@@

\begin{comment}
\section{Achknowledgements}
Mr William Rad\"unz would like to acknowledge the support from the Brazilian Research Council (CNPq) under the \textit{Science without Borders scholarship programme}. Mr Konstantinos Christou would like to acknowledge the support of the University of Aberdeen - College of Physical Science as well as the Aberdeen Formation Evaluation Society (\textit{AFES}). Last but not least credit should be given to both Dr Jefferson Gomes \& Dr Marcus Campell Bannerman, both lecturers at the University of Aberdeen, at the School of Engineering.
\end{comment}

@@

\end{comment}

>>>>

%%%%
%%%%  CHECK THIS BLOCK IF THE FILES ARE CORRECT ... CHANGED ON MAY 5TH
%%%%

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
  \includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
}
\hbox{\hspace{3.5cm}
  \includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
}
}     
\caption{Comparing test-cases of fixed and adaptive mesh while we have a dual inlet, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps}
\label{fig:3testcase_a}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Achknowledgements}
Mr William Rad\"unz would like to acknowledge the support from the Brazilian Research Council (CNPq) under the \textit{Science without Borders scholarship programme}. Mr Konstantinos Christou would like to acknowledge the support of the University of Aberdeen - College of Physical Science as well as the Aberdeen Formation Evaluation Society (\textit{AFES}).

@@
